Brief Announcement: Tight Bounds for Online Balanced Repartitioning

### 2020-02-18 paper/podc20ba.tex
Change the title: as in DISC

\title{Brief Announcement: Tight Bounds for Online Balanced Re-Partitioning}

@@

\begin{abstract}
Distributed   applications,  including  batch  processing, streaming, scale-out databases,
or machine learning, generate a significant amount of network traffic. By collocating frequently communicating nodes (e.g., virtual machines) on the same clusters (e.g., server or rack), the network load can be reduced and application performance improved. 
However, as the communication pattern is a priori unknown and may change over time, it needs to be learned efficiently, in an online manner.
%
This paper revisits the online 
balanced re-partitioning problem 
(introduced by Avin et al.~at DISC 2016)
which asks for an algorithm that strikes
an optimal tradeoff between the benefits
of collocation (i.e., lower network load) 
and its costs (i.e., migrations). 
%
Our first contribution is a significantly improved
lower bound of $\Omega(k\cdot \ell)$ on the
competitive ratio, where $\ell$ is the number
of clusters and $k$ is the cluster size,
even for a scenario in which the communication
pattern is static and can be perfectly partitioned;
we also provide a tight upper bound 
of $O(k\cdot \ell)$ for this scenario.
In addition, we present a tight upper bound
of $\Theta(\ell)$ for $k=3$,
for the general model in which the
communication pattern can change arbitrarily
over time. 
\end{abstract}

>>>>

\title{Brief Announcement: Tight Bounds for Online Balanced Repartitioning}

@@

\begin{abstract}
Distributed   applications,  including  batch  processing, streaming, scale-out databases,
or machine learning, generate a significant amount of network traffic. By collocating frequently communicating nodes (e.g., virtual machines) on the same clusters (e.g., server or rack), the network load can be reduced and application performance improved. 
However, as the communication pattern is a priori unknown and may change over time, it needs to be learned efficiently, in an online manner.
%
This paper revisits the online 
balanced repartitioning problem 
(introduced by Avin et al.~at DISC 2016)
which asks for an algorithm that strikes
an optimal tradeoff between the benefits
of collocation (i.e., lower network load) 
and its costs (i.e., migrations). 
%
Our first contribution is a significantly improved
lower bound of $\Omega(k\cdot \ell)$ on the
competitive ratio, where $\ell$ is the number
of clusters and $k$ is the cluster size,
even for a scenario in which the communication
pattern is static and can be perfectly partitioned;
we also provide a tight upper bound 
of $O(k\cdot \ell)$ for this scenario.
In addition, we present a tight upper bound
of $\Theta(\ell)$ for $k=3$,
for the general model in which the
communication pattern can change arbitrarily
over time. 
\end{abstract}
